---
title: "One way ANOVA - fertilizers"
author: "your name"
date: "the date"
toc: true
format: html
editor: visual
execute: 
  warning: false
  message: false
---

## Load packages
```{r}
library(tidyverse)
library(here)
library(cowplot)
library(janitor)
library(ggfortify)
```

## Load data
Save it in R as a data frame called `fertilizer`
```{r}
fertilizer <- here("data","fertilizer.csv") |>
  read_csv() |>
  clean_names() |>
  glimpse()
```

## Summarise data
```{r}
fertilizer_summary <- fertilizer |>
  group_by(fertilizer) |>
  summarise(n = n(), mean.yield = mean(yield), se.yield = sd(yield)/sqrt(n()))
fertilizer_summary
```

## Plot data
```{r}
fertilizer |>
  ggplot(aes(x = fertilizer, y = yield)) +
  geom_boxplot(fill = "grey80") +
  geom_jitter(width = 0.2, alpha = 0.5) +
  labs( x = "Fertilizer",
        y = "Yield") +
  theme_cowplot()
```

## Do an ANOVA analysis
```{r}
fertilizer.model <- lm(yield ~ fertilizer, data = fertilizer)
```

```{r}
autoplot(fertilizer.model) + theme_cowplot()
```

OK?

If so...

## Inspect the model: is there evidence of any difference between at leat one pair of fertilizers?
```{r}
anova(fertilizer.model)
```
## Inspect the model: effect sizes
```{r}
summary(fertilizer.model)
```
## Post-hoc test
```{r}
TukeyHSD(aov(yield ~ fertilizer, data = fertilizer))
```


So which fertilizers give significantly different yield from which others?
Which gives the greatest yield?